Outputs - civil servants' survey

### 2024-12-08 reports/paper_outputs_Dec_2024.qmd
clean code

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior)
exit_mod2 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
exit_mod3 <- exit_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
exit_mod4 <- exit_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1,exit_mod2,exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,#,
                  dv.labels = rep(c("Exit intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,5:6,3:4,1))

```{r}
voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)
voice_mod2 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
voice_mod3 <- voice_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
voice_mod4 <- voice_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(voice_mod1,voice_mod2,voice_mod3,voice_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Voice intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

```{r}
work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)
work_mod2 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION)
work_mod3 <- work_mod1 %>%  update(.~. + PROJECT_INFLUENCE)
work_mod4 <- work_mod1 %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(work_mod1,work_mod2,work_mod3,work_mod4,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Work effort intention"),each=4),
                  #dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2),
                  order.terms = c(2,6:7,3:5,1))

@@

```{r}
standardizedSolution_boot_ci(fit_all) %>% 
  #filter(op==":=") %>% 
  dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 
  mutate(across(2:4, round, 2)) %>% 
  mutate(across(5, round, 3)) %>% 
  gt::gt()
```

>>>>

@@

```{r}
standardizedSolution_boot_ci(fit_all) %>% 
  filter(op==":=") %>% 
  dplyr::select(label,est.std,boot.ci.lower,boot.ci.upper,pvalue) %>% 
  mutate(across(2:4, round, 2)) %>% 
  mutate(across(5, round, 3)) %>% 
  gt::gt()
```
